Enabling the Use of GPU Virtualization in Cloud Environments

### 2015-10-23 paper.tex
revision 6.5

\subsection{Discussion}
Again, the networking issue is restricting the performance of our executions, but it has been discussed during virtually all the paper.
However, it is not a new topic and in~\cite{tonithesis} is explained that improving the network infrastructure could make the difference.

The most remarkable achievement is the wide range of possible configuration and the freedom that would have an administrator to set and reset a system to fit the 
user requirements.

The requests of GPU-capable hosts in a completely transparent way for the user can be fulfilled with an small investment in infrastructure and in maintenance.
Energy can be saved, not only thanks to the remote access and the ability to emulate several GPUs from a real one, but also  by grouping the accelerators in a single machine (when possible) or turning down nodes when their GPUs are not necessary.

>>>>

\subsection{Discussion}
The network interconnect restricts the performance of our executions.
This is not a new topic and in~\cite{tonithesis} is explained that improving the network infrastructure could make a big different for GPU virtualization.

The most remarkable achievement is the wide range of possible configurations and the flexibility to set and reset a system to fit the 
user requirements.

With this virtualization technology, the requests for GPU devices can be fulfilled with small investments in infrastructure and maintenance.
Energy can be saved not only thanks to the remote access and the ability to emulate several GPUs from a real one, but also  by grouping the accelerators in a single machine (when possible) or turning down nodes when their GPUs are idle.
